### 2016-07-18 R/ITHIM.Rmd
Computes nonTravelMET matrix

```{r paameters}
parameters <- ddply(D, .(SEX), summarise,
             mean = mean(METs, na.rm=T),
             sd = sd(METs, na.rm=T)
             )
```

>>>>

```{r paameters}
parameters <- ddply(D, .(SEX, AGECAT), summarise,
             mean = mean(METs, na.rm=T),
             sd = sd(METs, na.rm=T)
             )

METmatrix <- rbind(matrix(0,nrow = 2, ncol = 2), matrix(parameters$mean, ncol = 2))
METmatrix <- METmatrix/METmatrix[3,2]
